---
title: "Multiverse Meta-Analysis Exploring the Efficacy of Psychological Interventions for Depression"
subtitle: "3. Descriptive Specification Plot"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(metafor)
library(plyr)
library(ggpubr)
library(grid)
library(gridExtra)
library(puniform)
library(svMisc)
library(cowplot) #Arrange Plots
library(ggrepel) #geom_label_repel

set.seed(1234)

PET.PEESE <- function(data) {
  mod <- list()
  fit_PET <- lm(yi ~ sqrt(vi), 
                weights = 1/vi, 
                data = data)
  
  pet_p <- coef(summary(fit_PET))["(Intercept)", "Pr(>|t|)"] # pet p-value < .10 -> peese
  
  if(pet_p >= .1) {
    mod$b <- coef(summary(fit_PET))["(Intercept)", "Estimate"] # pet estimate
    mod$ci.lb <- confint(fit_PET)["(Intercept)", "2.5 %"] 
    mod$ci.ub<- confint(fit_PET)["(Intercept)", "97.5 %"] 
    mod$pval <- pet_p
    mod$type <- "PET"
    
  }else{
    
    fit_PEESE <- lm(yi ~ vi, 
                    weights = 1/vi, 
                    data = data)
    
    mod$pval <- coef(summary(fit_PEESE))["(Intercept)", "Pr(>|t|)"] # pet p-value < .10 -> peese
    mod$b  <- coef(summary(fit_PEESE))["(Intercept)", "Estimate"] # peese estimate
    mod$ci.lb <- confint(fit_PEESE)["(Intercept)", "2.5 %"] 
    mod$ci.ub <- confint(fit_PEESE)["(Intercept)", "97.5 %"] 
    mod$type <- "PEESE"
    
  }
  return(mod)
}
```

# Setup

## Load

```{r}
data <- read_csv("data/tidy/data_cleaned.csv")

specifications_parallel <- read.csv2(file = "data/tidy/specifications_cleaned.csv")
```

<br>

## Cleaning Specifications
```{r}
# Remove combinations in specs_male which did not occur
specifications_full <- specifications_parallel[complete.cases(specifications_parallel), ]

# Only keep unique sample subsets resulting from "Which" factor combinations.
specifications_full <-
  specifications_full[!duplicated(specifications_full[, c("mean", "set", "ma_method")]),]

specifications_full <- specifications_full %>% filter(k >=10)

write.csv2(file = "data/tidy/specifications_cleaned.csv", 
           specifications_full)
```


```{r}
specifications_full <- specifications_full %>% 
  filter(dependency != "ignore") %>% 
  mutate(mean_corrected = ifelse(mean < 0, 0, mean ))
```

# Validating parallelization

Checking if mclapply produced the correct values. I check the smallest, largest, and 3 randomly drawn sets and recalculate the effect sizes manually.

### Smallest ES
```{r}
min_ma <- specifications_full %>% 
  filter(mean == min(mean))

data_min_ma <- data %>% 
  filter(row_number() %in% c(1,43,44,45,101,102,103,105,106,119,120,501,502,503,504,592,593,595,703,704,862,996))

dat_min <- data_min_ma %>% 
  escalc(yi=yi, vi=vi, data=.)

dat_min <- as.data.frame(aggregate(dat_min, 
                                   cluster = study,
                                   struct="CS" , #compound symmetric structure as nested are not indpendent
                                   rho = 0.5))
min_ma
PET.PEESE(dat_min)
```

### Largest ES
```{r}
max_ma <- specifications_full %>% filter(mean == max(mean))


data_max_ma <- data %>% slice(126,531,532,533,534,706,707,911,912,913,1069,1070,1071,1072,1073,1074)

mod_max <- rma.mv(data = data_max_ma, 
                  yi = yi, 
                  V = vi, 
                  method = "REML", 
                  control=list(optimizer="optim", optmethod="Nelder-Mead"),
                  random = list(~1 | es_id,
                                ~1 | study), 
                  sparse=TRUE)

max_ma
mod_max
```

### 3 Randomly drawn universes

```{r}
set.seed(42) # the answer to the Ultimate Question of Life, the Universe and Everything
specifications_sample <- specifications_full %>% sample_n(3) 
```

#### 1st sample
```{r}
specifications_sample[1,]
vec_1 <- c(specifications_sample[1,]$set)
vec_1 <- stringr::str_split(vec_1, pattern = ",")
vec_1 <- unlist(vec_1)
vec_1 <- as.numeric(vec_1)
data_sample_1 <- data %>% 
  filter(row_number() %in% c(vec_1))

data_sample_1 <- data_sample_1 %>% 
  escalc(yi=yi, vi=vi, data=.)

data_sample_1 <- as.data.frame(aggregate(data_sample_1, 
                                         cluster = study,
                                         struct="CS" , #compound symmetric structure as nested are not indpendent
                                         rho = 0.5))
rma(yi = data_sample_1$yi, vi = data_sample_1$vi, method = "FE") 
specifications_sample[1,]
```

#### 2nd sample
```{r}
specifications_sample[2,]
vec_2 <- c(specifications_sample[2,]$set)
vec_2 <- stringr::str_split(vec_2, pattern = ",")
vec_2 <- unlist(vec_2)
vec_2 <- as.numeric(vec_2)
data_sample_2 <- data %>% 
  filter(row_number() %in% c(vec_2))

data_sample_2 <- data_sample_2 %>% 
  escalc(yi=yi, vi=vi, data=.)

data_sample_2 <- as.data.frame(aggregate(data_sample_2, 
                                         cluster = study,
                                         struct="CS" , #compound symmetric structure as nested are not indpendent
                                         rho = 0.5))
PET.PEESE(data_sample_2)
specifications_sample[2,]
```

#### 3rd
```{r}
specifications_sample[3,]
vec_3 <- c(specifications_sample[3,]$set)
vec_3 <- stringr::str_split(vec_3, pattern = ",")
vec_3 <- unlist(vec_3)
vec_3 <- as.numeric(vec_3)
data_sample_3 <- data %>% 
  filter(row_number() %in% c(vec_3))

data_sample_3 <- data_sample_3 %>% 
  escalc(yi=yi, vi=vi, data=.)

data_sample_3 <- as.data.frame(aggregate(data_sample_3, 
                                         cluster = study,
                                         struct="CS" , #compound symmetric structure as nested are not indpendent
                                         rho = 0.5))
rma.uni(yi = data_sample_3$yi, 
        vi = data_sample_3$vi, method = "REML")
specifications_sample[3,]
```
<br>


# Inspecting Specifications

```{r}
specifications_full <- specifications_full %>% 
  filter(lb < 0)
specifications_full %>% glimpse()
```

## Overall

```{r}
specifications_full %>% 
  dplyr::summarise(mean_g = mean(mean),
                   min = min(mean),
                   max = max(mean),
                   mean_lb = mean(lb),
                   mean_ub = mean(ub),
                   n = n()) %>% 
  mutate(set = "full")
```

<br>

### type

```{r}
all_type_specs <- specifications_full %>% filter(type == "all types")

for (i in 1:10) {
  all_type_vec <- c(all_type_specs[i,]$set)
  all_type_vec <- stringr::str_split(all_type_vec, pattern = ",")
  all_type_vec <- unlist(all_type_vec)
  all_type_vec <- as.numeric(all_type_vec)
  result <- data %>% 
    filter(row_number() %in% c(all_type_vec)) %>% pull(type) %>% table() 
  print(result)
}
```


```{r}
specifications_full %>% 
  group_by(type) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

<br>

### control

```{r}
specifications_full %>% 
  group_by(control) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```
<br>

### target_group

```{r}
specifications_full %>% 
  group_by(target_group) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

### format
```{r}
specifications_full %>% 
  group_by(format) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

### diag
```{r}
specifications_full %>% 
  group_by(diagnosis) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```


### rob
```{r}
specifications_full %>% 
  group_by(rob) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```
<br>

### ma_method
```{r}
specifications_full %>% 
  group_by(ma_method) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max_g = max(mean),
                   min_g = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

<br>

### k
```{r}
specifications_full %>% 
  ggplot(aes(x = k)) + 
  geom_histogram(bins = 100) 
```

<br>

# Descriptive Specification Plot
## Preparation

<br>

### Which factors

```{r}
target_group <- c(unique(data$target_group), "all groups")
#region       <- str_to_lower(c(unique(data$region), "All Regions"))
format       <- c(unique(data$format), "all formats")
diagnosis    <- c(unique(data$diagnosis), "all diagnoses")
type         <- c(unique(data$type), "all types")
control      <- c(unique(data$control), "all control conditions")
rob          <- c("exclude_worst", "include_best", "all rob")
```


### How Factors
```{r}
ma_method    <- c("3-level", "rve",   # modeled
                  "reml", "fe", # aggregate | ignore
                  "p-uniform", "pet-peese")        # aggregate only
#dependency <- c("ignore", "aggregate", "modeled")

number_which_how_factors <- 10
```

### Rank each summary effect size by magnitude

```{r }
x_rank <- rank(specifications_full$mean, 
               ties.method = "random")
```


### Create all factors
```{r }
yvar <- rep(factor(rev(c(
  type,
  control,
  target_group,
  format,
  diagnosis,
  rob,
 # dependency,
  ma_method )), levels = rev(c(
    type,
    control,
    target_group,
    format,
    diagnosis,
    rob,
 #   dependency,
    ma_method ))), 
  times = nrow(specifications_full))

unique(yvar)
```


### Check lengths of yvar and specifications
```{r }
length(yvar)

length(levels(yvar)) * nrow(specifications_full)
```


```{r }
xvar <- rep(x_rank, 
            each = length(levels(yvar)))
spec <- NULL
```

<br>

### Determine which specifications are observed and which are not

```{r }
for(i in 1:nrow(specifications_full)) {
  id <- as.numeric(levels(yvar) %in% 
                     as.character(unlist(
                       specifications_full[i, 1:number_which_how_factors])))  
  spec <- c(spec, id)
}
```

## Universe specification panel
```{r }
plotdata <- data.frame(xvar, 
                       yvar, 
                       spec)

head(plotdata)
```

<br>

### Define y axis labels

Need to be in order of:
```{r}
rev(unique(yvar))
```

### Create which and how factor description
```{r }
ylabels <- rev(c(
  "Therapy: CBT-Based",  
  "Therapy: Non-CBT-Based",  
  "Therapy: All",  
  
  "Control: Usual Care",
  "Control: Other",
  "Control: Wait List", 
  "Control: All", 
  
  "Group: Adults", 
  "Group: General medical",
  "Group: Perinatal D.", 
  "Group: Older adults",
  "Group: Other groups",
  "Group: Student population",
  "Group: All groups", 
  
  "Format: Group", 
  "Format: Individual",
  "Format: Guided self-help",
  "Format: Other",
  "Format: All",
  
  "Diagnoses: Clinician", 
  "Diagnoses: Cut-off score",
  "Diagnoses: Subclinical D.",
  "Diagnoses: All diagnoses",
  
  #"Region: Europe", 
  #"Region: Other",
  #"Region: North America",
  #"Region: East Asia",
  #"Region: Australia",
  #"Region: All",
  
  "ROB: Worst Excluded",  
  "ROB: Only Best",
  "ROB: All rob", 
  
 # "Dependency: Ignore", 
 # "Dependency: Aggregate",
 # "Dependency: Modeled",
  
  "Method: 3-Level",
  "Method: RVE",
  "Method: REML",
  "Method: FE",
  "Method: p-uniform",
  "Method: PET-PEESE"
))

ylabels
```

<br>

```{r }
plotdata$k <- rep(specifications_full$k, 
                  each = length(levels(yvar)))  

plotdata$fill <- as.factor(plotdata$k * plotdata$spec)
```

```{r}
write.csv(plotdata, "data/tidy/plotdata.csv")
```

<br>

### Choose colors based on relative size (*k*)
```{r}
fill_quantiles <- quantile(plotdata$k, c(.10, .20, .30, .40, .50, .60, .70, .80, .90))
```

```{r}
plotdata_rel <- plotdata %>% 
  mutate(fill_manual = case_when(
    spec == 0 ~ 0,           # white
    k  != 0               & k <= fill_quantiles[1] ~ 1,     # light yellow
    k > fill_quantiles[1] & k <= fill_quantiles[2] ~ 2,
    k > fill_quantiles[2] & k <= fill_quantiles[3] ~ 3,
    k > fill_quantiles[3] & k <= fill_quantiles[4] ~ 4,
    k > fill_quantiles[4] & k <= fill_quantiles[5] ~ 5,
    k > fill_quantiles[5] & k <= fill_quantiles[6] ~ 6,
    k > fill_quantiles[6] & k <= fill_quantiles[7] ~ 7,
    k > fill_quantiles[7] & k <= fill_quantiles[8] ~ 8,
    k > fill_quantiles[8] & k <= fill_quantiles[9]  ~ 9,
    k > fill_quantiles[9]  ~ 10),   # dark red
    fill_manual = as.factor(fill_manual))
```

##### Choose colors

```{r }
cols <- RColorBrewer::brewer.pal(min(11, length(levels(plotdata_rel$fill_manual)) - 1), "Spectral")
plot(NULL, xlim=c(0,length(cols)), ylim=c(0,1), 
     xlab=cols, ylab="", xaxt="n", yaxt="n")
rect(0:(length(cols)-1), 0, 1:length(cols), 1, col=cols)
```

Turn on either this chunk to get warm = much evidence
```{r}
cols <- cols[floor(seq(from = length(cols), to = 0, # change from to to reverse color coding!
                       length.out = length(levels(plotdata_rel$fill_manual))))] # change - 1 for direction change
plot(NULL, xlim=c(0,length(cols)), ylim=c(0,1), 
     xlab="", ylab="", xaxt="n", yaxt="n")
rect(0:(length(cols)-1), 0, 1:length(cols), 1, col=cols)
```

<br>

We will need the length of each factor when we plot the spec curve:

```{r}
length_of_each_factor <- c(
  length(ma_method),
  length(rob) +  length(ma_method),
  length(diagnosis) + length(rob) +  length(ma_method) ,
  length(format) + length(diagnosis) + length(rob) +  length(ma_method) ,
  length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method),
  length(control) + length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method),
  length(type) + length(control) + length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method))
```

### Create Plot
```{r}
tile_plot <- ggplot(data = plotdata_rel, 
                    aes(x = xvar, 
                        y = as.factor(yvar), 
                        fill = fill_manual)) +
  geom_raster() + 
  geom_hline(yintercept = length_of_each_factor + 0.5) +  # Change lines here here
  scale_x_continuous(position = "bottom") +
  scale_y_discrete(labels = ylabels) +
  scale_fill_manual(
    values = c("white", cols)) +
  labs(x = "Specification number", 
       y = "Which/How factors") +
  coord_cartesian(
    expand = F, xlim = c(0.5, nrow(specifications_full) + 0.5)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.text.y = element_text(colour = "black", size = 8),
        axis.text.x = element_text(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        plot.margin = margin(t = 5.5, 
                             r = 5.5, 
                             b = 5.5, 
                             l = 5.5, 
                             unit = "pt"))

tile_plot
```

## Outcome curve plot
```{r}
fill_quantiles <- quantile(specifications_full$k, c(.10, .20, .30, .40, .50, .60, .70, .80, .90))

specifications_full_rel <- specifications_full %>% 
  mutate(fill_manual = case_when(
    k  != 0               & k <= fill_quantiles[1] ~ 1,     # light yellow
    k > fill_quantiles[1] & k <= fill_quantiles[2] ~ 2,
    k > fill_quantiles[2] & k <= fill_quantiles[3] ~ 3,
    k > fill_quantiles[3] & k <= fill_quantiles[4] ~ 4,
    k > fill_quantiles[4] & k <= fill_quantiles[5] ~ 5,
    k > fill_quantiles[5] & k <= fill_quantiles[6] ~ 6,
    k > fill_quantiles[6] & k <= fill_quantiles[7] ~ 7,
    k > fill_quantiles[7] & k <= fill_quantiles[8] ~ 8,
    k > fill_quantiles[8] & k <= fill_quantiles[9]  ~ 9,
    k > fill_quantiles[9]  ~ 10),   # dark red
    fill_manual = as.factor(fill_manual))

specifications_full_rel$xvar <- x_rank

yrng <- range(c(0, specifications_full$lb, specifications_full$ub))

#ylimit <- round(c(yrng[1] - diff(yrng)*0.1, yrng[2] + diff(yrng)*0.1), 1)
ylimit <- c(-.5, 2)

#y_breaks_forest <- round(seq(from = round(ylimit[1], 1), to = round(ylimit[2], 1), by = 0.5), 2)
y_breaks_forest <- seq(-.25, 2, 0.25)

y_labels_forest <- format(y_breaks_forest, nsmall = 2)
y_breaks_forest <- c(ylimit[1], y_breaks_forest)
y_labels_forest <- c(ylabels[which.max(nchar(ylabels))], y_labels_forest)
```

### Select specific meta-analyses to show in spec curve plot
```{r}
set.seed(42)
ma_for_forest_1 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "3-level") %>% mutate(label = "3-Level")

ma_for_forest_2 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "reml" & dependency == "aggregate") %>% mutate(label = "REML")

ma_for_forest_3  <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "pet-peese") %>% mutate(label = "PET-PEESE ")


ma_for_forest_4 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "fe" & dependency == "aggregate") %>% mutate(label = "FEM")

#ma_for_forest_4  <- specifications_full_rel %>% 
#  filter(ma_method == "reml" & target_group == "adults" ) %>%
#  arrange(desc(k)) %>% slice(1) %>% 
#  mutate(label = "REML (Only Adults)")

ma_for_forest_5  <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "p-uniform") %>% mutate(label = "p-uniform ")

ma_for_forest <- bind_rows(ma_for_forest_1,
                           ma_for_forest_2,
                           ma_for_forest_3,
                           ma_for_forest_4,
                           ma_for_forest_5)
```

### Create Plot
```{r}
spec_curve_plot <- specifications_full_rel %>% 
  # filter(!ma_method == "rve") %>% 
  ggplot(aes(x = xvar, 
             y = mean_corrected))+ 
  geom_errorbar(aes(ymin = lb, 
                    ymax = ub,
                    col = as.factor(fill_manual)), 
                size = .2,
                alpha = .7) +
  geom_line(col = "black", size = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.7) +
  geom_hline(yintercept = .24, linetype = "dotted", size = 0.7, color = "red") +
  #geom_hline(yintercept = .24, linetype = "dotted", size = 0.7, color = "red") +
  scale_x_continuous(name = "") +
  scale_y_continuous(name = expression(paste("Summary effect (", italic("g"),")")),
                     breaks = y_breaks_forest, labels = y_labels_forest) + 
  scale_color_manual(values = cols) +
  coord_cartesian(ylim = ylimit, xlim = c(0.5, nrow(specifications_full) + 0.5), expand = FALSE) +
  # ggtitle("Multiverse of All Reasonable Meta-Analyses") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(colour = c("white", rep("black", times = length(y_labels_forest) - 1))),
        axis.ticks.y = element_line(colour = c("white", rep("black", times = length(y_breaks_forest) - 1))),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(),
        panel.grid.minor.y = element_blank(),
        plot.margin = margin(t = 5.5, r = 5.5, b = -15, l = 5.5, unit = "pt")) +
  geom_point(data = ma_for_forest,
             color = "black") +
  geom_label_repel(data = ma_for_forest, 
                   aes(label = label),
                   seed = 42,
                   box.padding   = 0.35, 
                   point.padding = 0.5,
                   direction = "both",
                   lineheight = 2,
                   nudge_y = .5,
                   segment.color = 'black',
                   segment.angle = 90,
                   segment.size = .5)

spec_curve_plot
```

## Combine tile and specification curve plot
```{r}
descriptive_multiverse_plot <- plot_grid(spec_curve_plot,
                                         tile_plot,
                                         ncol = 1,
                                         align = "v",
                                         rel_heights = c(4,5))
descriptive_multiverse_plot
```

<br>

### Save Plot

```{r }
ggsave("figures/descriptive_specification.pdf", 
       descriptive_multiverse_plot, 
       width = 10, 
       height = 7.5,
       dpi = "retina"
)

ggsave("figures/descriptive_specification.png", 
       descriptive_multiverse_plot, 
       width = 10, 
       height = 7.5,
       dpi = "retina"
)
```

# Descriptive Specification Plot (only not-effective studies)

Here I produce a descriptive specification curve plot only for the meta-analyses suggesting that psychotherapy is not effective in treating depression (with the lower bound of the 95% CI being below zero)

<br>
## Preparation

<br>

### Which factors

```{r}
target_group <- c(unique(data$target_group), "all groups")
#region       <- str_to_lower(c(unique(data$region), "All Regions"))
format       <- c(unique(data$format), "all formats")
diagnosis    <- c(unique(data$diagnosis), "all diagnoses")
type         <- c(unique(data$type), "all types")
control      <- c(unique(data$control), "all control conditions")
rob          <- c("exclude_worst", "include_best", "all rob")
```


### How Factors
```{r}
ma_method    <- c("3-level", "rve",   # modeled
                  "reml", "fe", # aggregate | ignore
                  "p-uniform", "pet-peese")        # aggregate only
#dependency <- c("ignore", "aggregate", "modeled")

number_which_how_factors <- 10
```

### Rank each summary effect size by magnitude

```{r }
specifications_full <- specifications_full %>% 
  filter(lb <= 0)
```


# Inspecting Specifications

```{r}
specifications_full <- specifications_full %>% 
  filter(lb < 0)
specifications_full %>% glimpse()
```

## Overall

```{r}
specifications_full %>% 
  dplyr::summarise(mean_g = mean(mean),
                   min = min(mean),
                   max = max(mean),
                   mean_lb = mean(lb),
                   mean_ub = mean(ub),
                   n = n()) %>% 
  mutate(set = "full")
```

<br>

### type

```{r}
all_type_specs <- specifications_full %>% filter(type == "all types")

for (i in 1:10) {
  all_type_vec <- c(all_type_specs[i,]$set)
  all_type_vec <- stringr::str_split(all_type_vec, pattern = ",")
  all_type_vec <- unlist(all_type_vec)
  all_type_vec <- as.numeric(all_type_vec)
  result <- data %>% 
    filter(row_number() %in% c(all_type_vec)) %>% pull(type) %>% table() 
  print(result)
}
```


```{r}
specifications_full %>% 
  group_by(type) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

<br>

### control

```{r}
specifications_full %>% 
  group_by(control) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```
<br>

### target_group

```{r}
specifications_full %>% 
  group_by(target_group) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

### format
```{r}
specifications_full %>% 
  group_by(format) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

### diag
```{r}
specifications_full %>% 
  group_by(diagnosis) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```


### rob
```{r}
specifications_full %>% 
  group_by(rob) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```
<br>

### ma_method
```{r}
specifications_full %>% 
  group_by(ma_method) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max_g = max(mean),
                   min_g = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n = n())
```

<br>

### k
```{r}
specifications_full %>% 
  ggplot(aes(x = k)) + 
  geom_histogram(bins = 100) 
```

```{r }
x_rank <- rank(specifications_full$mean, 
               ties.method = "random")
```


### Create all factors
```{r }
yvar <- rep(factor(rev(c(
  type,
  control,
  target_group,
  format,
  diagnosis,
  rob,
 # dependency,
  ma_method )), levels = rev(c(
    type,
    control,
    target_group,
    format,
    diagnosis,
    rob,
 #   dependency,
    ma_method ))), 
  times = nrow(specifications_full))

unique(yvar)
```


### Check lengths of yvar and specifications
```{r }
length(yvar)

length(levels(yvar)) * nrow(specifications_full)
```


```{r }
xvar <- rep(x_rank, 
            each = length(levels(yvar)))
spec <- NULL
```

<br>

### Determine which specifications are observed and which are not

```{r }
for(i in 1:nrow(specifications_full)) {
  id <- as.numeric(levels(yvar) %in% 
                     as.character(unlist(
                       specifications_full[i, 1:number_which_how_factors])))  
  spec <- c(spec, id)
}
```

## Universe specification panel
```{r }
plotdata <- data.frame(xvar, 
                       yvar, 
                       spec)

head(plotdata)
```

<br>

### Define y axis labels

Need to be in order of:
```{r}
rev(unique(yvar))
```

### Create which and how factor description
```{r }
ylabels <- rev(c(
  "Therapy: CBT-Based",  
  "Therapy: Non-CBT-Based",  
  "Therapy: All",  
  
  "Control: Usual Care",
  "Control: Other",
  "Control: Wait List", 
  "Control: All", 
  
  "Group: Adults", 
  "Group: General medical",
  "Group: Perinatal D.", 
  "Group: Older adults",
  "Group: Other groups",
  "Group: Student population",
  "Group: All groups", 
  
  "Format: Group", 
  "Format: Individual",
  "Format: Guided self-help",
  "Format: Other",
  "Format: All",
  
  "Diagnoses: Clinician", 
  "Diagnoses: Cut-off score",
  "Diagnoses: Subclinical D.",
  "Diagnoses: All diagnoses",
  
  #"Region: Europe", 
  #"Region: Other",
  #"Region: North America",
  #"Region: East Asia",
  #"Region: Australia",
  #"Region: All",
  
  "ROB: Worst Excluded",  
  "ROB: Only Best",
  "ROB: All rob", 
  
 # "Dependency: Ignore", 
 # "Dependency: Aggregate",
 # "Dependency: Modeled",
  
  "Method: 3-Level",
  "Method: RVE",
  "Method: REML",
  "Method: FE",
  "Method: p-uniform",
  "Method: PET-PEESE"
))

ylabels
```

<br>

```{r }
plotdata$k <- rep(specifications_full$k, 
                  each = length(levels(yvar)))  

plotdata$fill <- as.factor(plotdata$k * plotdata$spec)
```

```{r}
#write.csv(plotdata, "data/tidy/plotdata.csv")
```

<br>

### Choose colors based on relative size (*k*)
```{r}
fill_quantiles <- quantile(plotdata$k, c(.10, .20, .30, .40, .50, .60, .70, .80, .90))
```

```{r}
plotdata_rel <- plotdata %>% 
  mutate(fill_manual = case_when(
    spec == 0 ~ 0,           # white
    k  != 0               & k <= fill_quantiles[1] ~ 1,     # light yellow
    k > fill_quantiles[1] & k <= fill_quantiles[2] ~ 2,
    k > fill_quantiles[2] & k <= fill_quantiles[3] ~ 3,
    k > fill_quantiles[3] & k <= fill_quantiles[4] ~ 4,
    k > fill_quantiles[4] & k <= fill_quantiles[5] ~ 5,
    k > fill_quantiles[5] & k <= fill_quantiles[6] ~ 6,
    k > fill_quantiles[6] & k <= fill_quantiles[7] ~ 7,
    k > fill_quantiles[7] & k <= fill_quantiles[8] ~ 8,
    k > fill_quantiles[8] & k <= fill_quantiles[9]  ~ 9,
    k > fill_quantiles[9]  ~ 10),   # dark red
    fill_manual = as.factor(fill_manual))
```

##### Choose colors

```{r }
cols <- RColorBrewer::brewer.pal(min(11, length(levels(plotdata_rel$fill_manual)) - 1), "Spectral")
plot(NULL, xlim=c(0,length(cols)), ylim=c(0,1), 
     xlab=cols, ylab="", xaxt="n", yaxt="n")
rect(0:(length(cols)-1), 0, 1:length(cols), 1, col=cols)
```

Turn on either this chunk to get warm = much evidence
```{r}
cols <- cols[floor(seq(from = length(cols), to = 0, # change from to to reverse color coding!
                       length.out = length(levels(plotdata_rel$fill_manual))))] # change - 1 for direction change
plot(NULL, xlim=c(0,length(cols)), ylim=c(0,1), 
     xlab="", ylab="", xaxt="n", yaxt="n")
rect(0:(length(cols)-1), 0, 1:length(cols), 1, col=cols)
```

<br>

We will need the length of each factor when we plot the spec curve:

```{r}
length_of_each_factor <- c(
  length(ma_method),
  length(rob) +  length(ma_method),
  length(diagnosis) + length(rob) +  length(ma_method) ,
  length(format) + length(diagnosis) + length(rob) +  length(ma_method) ,
  length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method),
  length(control) + length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method),
  length(type) + length(control) + length(target_group) +  length(format) + length(diagnosis) + length(rob) +  length(ma_method))
```

### Create Plot
```{r}
tile_plot <- ggplot(data = plotdata_rel, 
                    aes(x = xvar, 
                        y = as.factor(yvar), 
                        fill = fill_manual)) +
  geom_raster() + 
  geom_hline(yintercept = length_of_each_factor + 0.5) +  # Change lines here here
  scale_x_continuous(position = "bottom") +
  scale_y_discrete(labels = ylabels) +
  scale_fill_manual(
    values = c("white", cols)) +
  labs(x = "Specification number", 
       y = "Which/How factors") +
  coord_cartesian(
    expand = F, xlim = c(0.5, nrow(specifications_full) + 0.5)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.text.y = element_text(colour = "black", size = 8),
        axis.text.x = element_text(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        plot.margin = margin(t = 5.5, 
                             r = 5.5, 
                             b = 5.5, 
                             l = 5.5, 
                             unit = "pt"))

tile_plot
```

## Outcome curve plot
```{r}
fill_quantiles <- quantile(specifications_full$k, c(.10, .20, .30, .40, .50, .60, .70, .80, .90))

specifications_full_rel <- specifications_full %>% 
  mutate(fill_manual = case_when(
    k  != 0               & k <= fill_quantiles[1] ~ 1,     # light yellow
    k > fill_quantiles[1] & k <= fill_quantiles[2] ~ 2,
    k > fill_quantiles[2] & k <= fill_quantiles[3] ~ 3,
    k > fill_quantiles[3] & k <= fill_quantiles[4] ~ 4,
    k > fill_quantiles[4] & k <= fill_quantiles[5] ~ 5,
    k > fill_quantiles[5] & k <= fill_quantiles[6] ~ 6,
    k > fill_quantiles[6] & k <= fill_quantiles[7] ~ 7,
    k > fill_quantiles[7] & k <= fill_quantiles[8] ~ 8,
    k > fill_quantiles[8] & k <= fill_quantiles[9]  ~ 9,
    k > fill_quantiles[9]  ~ 10),   # dark red
    fill_manual = as.factor(fill_manual))

specifications_full_rel$xvar <- x_rank

yrng <- range(c(0, specifications_full$lb, specifications_full$ub))

#ylimit <- round(c(yrng[1] - diff(yrng)*0.1, yrng[2] + diff(yrng)*0.1), 1)
ylimit <- c(-.5, 2)

#y_breaks_forest <- round(seq(from = round(ylimit[1], 1), to = round(ylimit[2], 1), by = 0.5), 2)
y_breaks_forest <- seq(-.25, 2, 0.25)

y_labels_forest <- format(y_breaks_forest, nsmall = 2)
y_breaks_forest <- c(ylimit[1], y_breaks_forest)
y_labels_forest <- c(ylabels[which.max(nchar(ylabels))], y_labels_forest)
```

### Select specific meta-analyses to show in spec curve plot
```{r}
set.seed(42)
ma_for_forest_1 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "3-level") %>% mutate(label = "3-Level")

ma_for_forest_2 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "reml" & dependency == "aggregate") %>% mutate(label = "REML")

ma_for_forest_3  <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "pet-peese") %>% mutate(label = "PET-PEESE ")


ma_for_forest_4 <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "fe" & dependency == "aggregate") %>% mutate(label = "FEM")

#ma_for_forest_4  <- specifications_full_rel %>% 
#  filter(ma_method == "reml" & target_group == "adults" ) %>%
#  arrange(desc(k)) %>% slice(1) %>% 
#  mutate(label = "REML (Only Adults)")

ma_for_forest_5  <- specifications_full_rel %>% 
  filter(full_set == 1 & ma_method == "p-uniform") %>% mutate(label = "p-uniform ")

ma_for_forest <- bind_rows(ma_for_forest_1,
                           ma_for_forest_2,
                           ma_for_forest_3,
                           ma_for_forest_4,
                           ma_for_forest_5)
```

### Create Plot
```{r}
spec_curve_plot <- specifications_full_rel %>% 
  # filter(!ma_method == "rve") %>% 
  ggplot(aes(x = xvar, 
             y = mean))+ 
  geom_errorbar(aes(ymin = lb, 
                    ymax = ub,
                    col = as.factor(fill_manual)), 
                size = .2,
                alpha = .7) +
  geom_line(col = "black", size = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.7) +
  geom_hline(yintercept = .24, linetype = "dotted", size = 0.7, color = "red") +
  #geom_hline(yintercept = .24, linetype = "dotted", size = 0.7, color = "red") +
  scale_x_continuous(name = "") +
  scale_y_continuous(name = expression(paste("Summary effect (", italic("g"),")")),
                     breaks = y_breaks_forest, labels = y_labels_forest) + 
  scale_color_manual(values = cols) +
  coord_cartesian(ylim = ylimit, xlim = c(0.5, nrow(specifications_full) + 0.5), expand = FALSE) +
  # ggtitle("Multiverse of All Reasonable Meta-Analyses") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(colour = c("white", rep("black", times = length(y_labels_forest) - 1))),
        axis.ticks.y = element_line(colour = c("white", rep("black", times = length(y_breaks_forest) - 1))),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(),
        panel.grid.minor.y = element_blank(),
        plot.margin = margin(t = 5.5, r = 5.5, b = -15, l = 5.5, unit = "pt")) +
  geom_point(data = ma_for_forest,
             color = "black") +
  geom_label_repel(data = ma_for_forest, 
                   aes(label = label),
                   seed = 42,
                   box.padding   = 0.35, 
                   point.padding = 0.5,
                   direction = "both",
                   lineheight = 2,
                   nudge_y = .5,
                   segment.color = 'black',
                   segment.angle = 90,
                   segment.size = .5)

spec_curve_plot
```

## Combine tile and specification curve plot
```{r}
descriptive_multiverse_plot <- plot_grid(spec_curve_plot,
                                         tile_plot,
                                         ncol = 1,
                                         align = "v",
                                         rel_heights = c(4,5))
descriptive_multiverse_plot
```

<br>
