---
title: "Multiverse Meta-Analysis Exploring the Efficacy of Psychological Interventions for Depression"
subtitle: "1. Data Cleaning"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      encoding = encoding, 
      output_dir = "html") })
      rmarkdown::render(inputFile, 
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: lumen
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(metafor)
library(plyr)
library(ggpubr)
library(grid)
library(gridExtra)
library(puniform)
library(metapsyTools)
set.seed(1234)

# helper functions
checkVariable <- function(data, variable) {
  data  %>% pull({{variable}}) %>% table(useNA = "always")
}
```

# Loading

```{r}
data_2022_raw <- read_excel("data/raw/data-depression-psyctr-2022.xlsx") 
```

<br>

# Initial Cleaning
```{r}
data_2022 <- data_2022_raw %>% 
  mutate(vi = .g_se^2,
         yi = .g,
         es_id = row_number()) %>% # each effect size gets unique ID
  filter(!is.na(yi)) %>% 
  group_by(study) %>% 
  mutate(study_id = group_indices()) %>% 
  select(study_id, es_id, study, yi, vi, sei = .g_se, everything()) %>% 
  ungroup() 
```

<br>

# Cleaning Specifications

The different which factors are ordered after the PICOs format:

+ P: target_group, country

+ I: format, type

+ C: control

+ O: diag

+ s: risk of bias


<br>

## Which factors

### target_group

**Original categories from `target_group` variable (codebook):**
1. Adults
2. Older adults
3. Student population 
4. Women with PPD
5. General medical
6. Other
7. Children and adolescents

**New categories from BMJ registration**
1) adults (adults in general with no specific demographic characteristic)
2) general medical group
3) perinatal depression
4) student population
5) older adults
6) other groups
or 7) all target groups.


```{r}
data_2022 %>% checkVariable(target_group) 

data_2022_target_group <- data_2022 %>% 
  mutate(target_group = case_when(
    target_group == "4 & 5" & study == "Zhao, 2019" ~ "perinatal depression", # Zhao, 2019 is both general medical and perinatal depression, I recoded it as perinatal depression as this was the main focus of the study.
    TRUE ~ target_group)) %>% 
  mutate(
    target_group = recode(target_group, "adul"     = "adults"),
    target_group = recode(target_group, "yadul"     = "adults"),
    target_group = recode(target_group, "old"     = "older adults"),
    target_group = recode(target_group, "stud"     = "student population"),
    target_group = recode(target_group, "ppd"     = "perinatal depression"),
    target_group = recode(target_group, "med"     = "general medical"),
    target_group = recode(target_group, "oth"     = "other target groups"))

data_2022_target_group %>% checkVariable(target_group) 
```

<br>

```{r}
target_group <- c(unique(data_2022_target_group$target_group), "all groups")

target_group
```

<br>

##### Loop

```{r eval = FALSE}
if(specifications$target_group[i] == "adults") {
  dat <- dat[dat$target_group == "adults", ] 
} else {
  if(specifications$target_group[i] == "general medical") {
    dat <- dat[dat$target_group == "general medical", ] 
  } else {
    if(specifications$target_group[i] == "perinatal depression") {
      dat <- dat[dat$target_group == "perinatal depression", ] 
    } else {
      if(specifications$target_group[i] == "older adults") {
        dat <- dat[dat$target_group == "older adults", ] 
      } else {
        if(specifications$target_group[i] == "other target groups") {
          dat <- dat[dat$target_group == "other target groups", ]   
        } else {
          if(specifications$target_group[i] == "student population") {
            dat <- dat[dat$target_group == "student population", ] 
          }
        }
      }
    }
  }
}
```

<br>

##### Labels

```{r eval = FALSE}
"Group: Adults", 
"Group: General medical",
"Group: Perinatal depression", 
"Group: Student population",
"Group: Older adults",
"Group: Other groups",
"Group: All groups", 
```

<br>

###	format

Original categories `format` (codebook):
1. Individual
2. Group
3. Guided self-help
4. Telephone
5. Couple therapy 
6. Other

BMJ categories
1) group
2) individual
3) guided self-help
4) couples
5) telephone
6) other formats
7) all formats.

Combined categories
1) group
2) individual
3) guided self-help
4) other formats(other, telephone, couples)
5) all formats

```{r}
data_2022_target_group %>% checkVariable(format) 

data_2022_format <- data_2022_target_group %>% 
    mutate(format = recode(format, "ind" = "individual"),
           format = recode(format, "grp" = "group"),
           format = recode(format, "gsh" = "guided self-help"),
           format = recode(format, "ush" = "other formats"),
           format = recode(format, "tel" = "other formats"),
           format = recode(format, "oth" = "other formats"),
           format = recode(format, "cpl" = "other formats"))

data_2022_format %>% checkVariable(format) 
```


```{r}
format <- c(unique(data_2022_format$format), "all formats")

format
```

<br>

##### Loop
```{r eval = FALSE}
if(specifications$format[i] == "group") {
  dat <- dat[dat$format == "group", ] 
} else {
  if(specifications$format[i] == "individual") {
    dat <- dat[dat$format == "individual", ] 
  } else {
    if(specifications$format[i] == "guided self-help") {
      dat <- dat[dat$format == "guided self-help", ] 
    } else {
      if(specifications$format[i] == "other formats") {
        dat <- dat[dat$format == "other formats", ] 
      }
    }
  }
}
```

<br>

##### Labels

<br>

```{r eval = FALSE}
"Format: Group",
"Format: Individual",
"Format: Guided self-help",
"Format: Other",
"Format: All",
```

<br>

### diagnosis

Original `diag` categories (codebook):

1. Major depression
2. Mood disorder 
3. Cut-off score
4. Subclinical depression
5. Chronic depression

BMJ 
1). major depression according to criteria by DSM-V, DSM-IV, DSM-III- R, DSM-III, Research Diagnostic Criteria (RDC) for major depression, or Feighner criteria for depressive disorder. 
2.) mood disorder or other diagnosed disorders (e.g., dysthymia; depression Not Otherwise Specified (NOS); minor depression according to Research Diagnostic Criteria). 
3). Chronic depression, i.e., participants meet criteria for chronic or treatment-resistant depression, according to any definition given by the authors of the study. We also include diagnoses defined as 
4). scoring above a clinically relevant cutoff score, or 
5) diagnosed subclinical depression, i.e. participants score above a cut-off on a self-rating scale, but do not meet criteria for a depressive disorder according to a diagnostic interview (such as the MINI, CIDI or SCID). 
6) all diagnoses

**New categories:**

1) diagnosis (major, mood, chronic)
2) cut-off score (cut-off score)
4) subclinical depression
3) all diagnoses

```{r}
data_2022_diagnosis <- data_2022_format

table(data_2022_diagnosis$diagnosis)
```

```{r}
data_2022_format %>% checkVariable(diagnosis)

data_2022_diagnosis <- data_2022_format %>%
  mutate(diagnosis = recode(diagnosis, "mdd" = "diagnosis"),
         diagnosis = recode(diagnosis, "mood" = "diagnosis"),
         diagnosis = recode(diagnosis, "cut" = "cut-off score"),
         diagnosis = recode(diagnosis, "sub" = "subclinical depression"),
         diagnosis = recode(diagnosis, "chr" = "diagnosis"))

data_2022_diagnosis %>% checkVariable(diagnosis)
```


```{r}
diagnosis<- c(unique(data_2022_diagnosis$diagnosis), "all diagnoses")

diagnosis
```

<br>

##### Loop

<br>

```{r eval = FALSE}
    if(specifications$diagnosis[i] == "diagnosis") {
    dat <- dat[dat$diagnosis== "diagnosis", ] 
  } else {
    if(specifications$diagnosis[i] == "cut-off score") {
      dat <- dat[dat$diagnosis== "cut-off score", ] 
    } else {
    if(specifications$diagnosis[i] == "subclinical depression") {
      dat <- dat[dat$diagnosis== "subclinical depression", ] 
    }
    }
  }
```

<br>

##### Labels

<br>

```{r eval = FALSE}
"Diagnoses: Diagnoses",
"Diagnoses: Cut-off score",
"Diagnoses: Subclinical Depressen",
"Diagnoses: All diagnoses",
```

<br>

### type

1) cognitive behavior therapy, 
2) problem-solving therapy, 
3) third-wave cognitive therapies, 
4) behavioral activation therapy,
5) nondirective supportive therapy, 
6) psychodynamic therapy, 
7) interpersonal therapy, 
8) life review therapy, 
9) other types of therapy, or 
10) all types of therapy. 

New categories:

1. Cbt-based approaches (cbt, pst, 3rd wave, bat) 
2. Not-cbt-based approaches (psychodynamic, interpersonal, life review, other)

```{r}
data_2022_diagnosis %>% checkVariable(condition_arm1)

data_2022_type <- data_2022_diagnosis %>% 
  mutate( type = condition_arm1,
          type = recode(type, "cbt"   = "cbt-based"),
          type = recode(type, "pst"   = "cbt-based"),
          type = recode(type, "3rd"   = "cbt-based"),
          type = recode(type, "bat"   = "cbt-based"),
          type = recode(type, "dyn"   = "not-cbt-based"),
          type = recode(type, "ipt"   = "not-cbt-based"),
          type = recode(type, "lrt"   = "not-cbt-based"),
          type = recode(type, "sup"   = "not-cbt-based"),
          type = recode(type, "other psy" = "not-cbt-based"))

data_2022_type %>% checkVariable(type)
```

```{r}
type <- c(unique(data_2022_type$type), "all types")
type
```

<br>

##### Loop

<br>

```{r eval = FALSE}
    if(specifications$type[i] == "cbt-based") {
    dat <- dat[dat$type == "cbt-based", ] 
  } else {
    if(specifications$type[i] == "not-cbt-based") {
      dat <- dat[dat$type == "not-cbt-based", ] 
    }
  }
```

<br>

##### Labels

<br>

```{r eval = FALSE}
"Type: CBT-based",
"Type: Not-CBT-based",
"Type: All interventions",
```

<br>

###	control

1) care as usual
2) waiting list
3) other types of control conditions
4) all types of control conditions.

```{r}
data_2022_type %>% checkVariable(condition_arm2)
data_2022_control <- data_2022_type %>% 
  mutate(control = condition_arm2) 
table(data_2022_control$control)
```

```{r}
control <- c(unique(data_2022_control$control), "all control conditions")

control
```

<br>

##### Loop

<br>

```{r eval = FALSE}
  if(specifications$control[i] == "wl") {
    dat <- dat[dat$control == "wl", ] 
  } else {
    if(specifications$control[i] == "cau") {
      dat <- dat[dat$control == "cau", ] 
    } else {
      if(specifications$control[i] == "other ctr") {
        dat <- dat[dat$control == "other ctr", ] 
      }
    }
  }
```

<br>

##### Labels

<br>

```{r eval = FALSE}
"Control: Care as usual",
"Control: Waitlist",
"Control: Other",
"Control: All", 
```

<br>

###	region

Codebook?
1) EU
2) the USA
3) the UK
4) Canada
5) East Asia
6) Australia
7) other countries
8) all countries.

New categories
1) North America (1, 4)
2) Europe (including UK; 2, 3) 
3) East Asia
4) Australia
5) Other (5, 6, 7)

```{r}
data_2022_control %>% checkVariable(country)
data_2022_country <- data_2022_control %>% 
  mutate(region = case_when(
    country == "can" ~ "North America",
    country == "uk" ~ "Europe",
    country == "eu" ~ "Europe",
    country == "us" ~ "North America",
    country == "au" ~ "Australia",
    country == "eas" ~ "East Asia",
    country == "oth" ~ "Other Region"))

table(data_2022_country$region)
```

```{r}
region <- str_to_lower(c(unique(data_2022_country$region), "All Regions"))

region
```

<br>

##### Loop

```{r eval = FALSE}
    if(specifications$region[i] == "europe") {
    dat <- dat[dat$region == "europe", ] 
  } else {
    if(specifications$region[i] == "other region") {
      dat <- dat[dat$region == "other region", ] 
    } else {
      if(specifications$region[i] == "north america") {
        dat <- dat[dat$region == "north america", ] 
      } else {
      if(specifications$region[i] == "east asia") {
        dat <- dat[dat$region == "east asia", ] 
      } else {
      if(specifications$region[i] == "australia") {
        dat <- dat[dat$region == "australia", ] 
      }
    }
      }
    } 
```

<br>

##### Labels

<br>

```{r eval = FALSE}
"Region: Europe",
"Region: North America",
"Region: East Asia",
"Region: Australia",
"Region: Other",
"Region: All",
```

<br>

### risk_of_bias

1) low risk of bias (if each aspect is rated as low risk)  
2) some concern (if any aspect is rated as high risk). 
3) high risk of bias (if all aspects are rated as high risk). 
3) all studies, regardless of bias assessment.

```{r}
data_2022_country %>% checkVariable(rob)
data_2022_rob <- data_2022_country %>% 
  mutate(risk_of_bias = recode(rob, 
                               "4" = "Low", 
                               "0" = "High", 
                               "1" = "Some Concern", 
                               "2" = "Some Concern", 
                               "3" = "Some Concern"))

table(data_2022_rob$risk_of_bias)
```

Risk of bias ranging from 0 (high) to 4 (low) is trichotomized into low (4) , high (0) and other (1-3).

```{r}
risk_of_bias <- str_to_lower(c(unique(data_2022_rob$risk_of_bias), "All risk of biases"))
risk_of_bias
```

##### Loop

```{r eval = FALSE}
  if(specifications$risk_of_bias[i] == "low") {
    dat <- dat[dat$risk_of_bias == "low", ] 
  } else {
    if(specifications$risk_of_bias[i] == "some concern") {
      dat <- dat[dat$risk_of_bias == "some concern", ] 
  } else {
    if(specifications$risk_of_bias[i] == "high") {
      dat <- dat[dat$risk_of_bias == "high", ] 
    }
  }
```

<br>

##### Labels

```{reval = FALSE}
"Risk of Bias: Low",
"Risk of Bias: Some Concern",
"Risk of Bias: High",
"Risk of Bias: All",
```


<br>

# Potential new meta-analytical which factors

These are some ideas for additional which factors, but not implemented in the current publication.
## outliers

These studies are identified outliers with their respective 95% CIs outside the 95% prediction interval calculated with a 3-Level REML model.

### CI outside PI
```{r}
ma_3lvl <- data_2022_rob %>% 
  rma.mv(data = ., 
         yi = yi, 
         V = vi, 
         method = "REML", 
         control=list(optimizer = "optim", optmethod="Nelder-Mead"),
         random = list(~1 | es_id,
                       ~1 | study_id), 
         sparse=TRUE)

prediction_interval_lb <- predict(ma_3lvl)$pi.lb
prediction_interval_ub <- predict(ma_3lvl)$pi.ub

ci_lower <- ma_3lvl$yi - 1.96*sqrt(ma_3lvl$vi) 
ci_upper <-  ma_3lvl$yi + 1.96*sqrt(ma_3lvl$vi)

data_2022_outlier <- data_2022_rob %>% 
  cbind(ci_lower, ci_upper) %>% 
  relocate(study, yi, ci_lower, ci_upper) %>% 
  mutate(outlier = case_when(
    ci_lower > prediction_interval_ub |ci_upper < prediction_interval_lb ~ "ci outside pi",
    TRUE ~ "no outlier"
      ),
    outlier) %>% 
    relocate(id_study, yi,outlier, ci_lower, ci_upper) 
```





```{r}
outlier <- str_to_lower(c(unique(data_2022_outlier$outlier), "All studies"))
outlier
```

##### Loop

```{r eval = FALSE}
  if(specifications$outlier[i] == "no outlier") {
    dat <- dat[dat$outlier == "no outlier", ] 
  } else {
    if(specifications$outlier[i] == "ci outside pi") {
      dat <- dat[dat$outlier == "ci outside pi", ] 
    }
  }
```

### CI outside 1.5 SD

```{r}
data_2022_outlier <- data_2022_outlier %>% 
  mutate(outlier_1.5_sd = ifelse(yi > 1.5, "outlier > 1.5 sd", "no outlier"))
```

<br>

## multiple_outcome_types

Some studies contain multiple outcome types, ie. Hedges g based on means, sd, n and dichotomous outcomes, or change scores. It could be interesting to see, whether it makes a difference if including all effect sizes that could be calculated or keeping only one type of 


```{r}
data_2022_multiple_outcome_types <- filterPriorityRule(data_2022_outlier,
                                                       outcome_type = c("msd", "response", "remission", "other dich", "change", "other statistic"),
                                                       .study.indicator = "study")
```

```{r}
data_2022_one_outcome <- data_2022_outlier %>% 
    filter(.id %in% data_2022_multiple_outcome_types$.id) %>% 
    mutate(multiple_outcome_types = "select one outcome type")

data_2022_multiple_outcomes <- data_2022_outlier %>% 
  filter(!.id %in% data_2022_multiple_outcome_types$.id) %>%  
  mutate(multiple_outcome_types = "select all outcome types") %>% 
  relocate(id_study, multiple_outcome_types, outcome_type)

data_2022_multiple_outcome_types_joined <- bind_rows(data_2022_one_outcome, data_2022_multiple_outcomes )  %>% 
  arrange(id_study) %>% 
  relocate(id_study, multiple_outcome_types, outcome_type) 

table(data_2022_multiple_outcome_types_joined$multiple_outcome_types)
```

<br>


```{r eval = FALSE}
  if(specifications$multiple_outcome_types[i] == "select one outcome type") {
    dat <- dat[dat$multiple_outcome_types == "select all outcome types", ] 
  }
```

```{r}
multiple_outcome_types <- str_to_lower(c(unique(data_2022_multiple_outcome_types_joined$multiple_outcome_types), "All outcomes"))
multiple_outcome_types
```

<br>

## How factors

```{r define-how-factors}
ma_method <- c("3-level", "rve", "reml", "fe", "pet-peese", "p-uniform")
```

<br>

# Total number of which factor combinations

P: target_group, country
I: type, format
C: control
O: diagnosis
s: risk of bias, outliers, outcome_types

```{r}
# P
length(target_group) * 
# I
  length(type) * length(format) *
# C
  length(control) *
# O
  length(diagnosis) *
# S
  length(risk_of_bias) * length(ma_method)  * length(outlier) #* length(multiple_outcome_types)
```

<br>

# Comparing data with multiple outcome types and a single outcome type

## Data with multiple outcome types
```{r}
data <- mutate_all(data_2022_rob, 
                   funs(str_to_lower)) %>% 
  mutate(n_1 = as.numeric(ifelse(is.na(n_arm1), totaln_arm1, n_arm1)),
         n_2 = as.numeric(ifelse(is.na(n_arm2), totaln_arm1, n_arm2)),
         sample_size = n_1 + n_2,
         es_id = row_number() ,
         rob_include_best = ifelse(risk_of_bias == "low", 1, 0),
         rob_exclude_worst = ifelse(risk_of_bias %in% c("low", "some concern"), 1, 0)) %>% 
  select(study,
         es_id,
         yi, vi, sei,
         target_group, 
         format,
         diagnosis, 
         type,
         control, 
         region, 
         risk_of_bias, 
         rob,
         rob_include_best,
         rob_exclude_worst,
         n_1, 
         n_2,
         sample_size)

data$vi <- as.numeric(data$vi)
data$yi <- as.numeric(data$yi)
data$sei <- as.numeric(data$sei)

data
```


### as.factor()
```{r}
data <- data %>% 
  mutate_if(names(.) %in% c("target_group","diagnosis","format", "type", "rob", "control", "condition_arm1", "condition_arm2", "outcome_type", "rating" ), funs(as.factor(.)))

summary(data)
```

### Sample size

Individuals should be counted for the sample size and not multiple outcomes per person. Therefore I group by each study and keep only distinct sample sizes.

```{r}
sample_size_data <- data %>% 
  group_by(study) %>%
  distinct(sample_size) %>% 
  plyr::summarise(sample_size_sum = sum(sample_size, na.rm = T),
            sample_size_median = median(sample_size, na.rm = T),
            sample_size_mean = mean(sample_size, na.rm = T)) 

sample_size_data
```

```{r}
data %>% 
  group_by(study) %>%
  distinct(sample_size) %>% print(n=701)
```


<br>

### Included primary studies
```{r}
unique_studies <- length(unique(data$study))
unique_studies
```

<br>

### Effect size distribution
```{r}
data %>% 
  dplyr::summarise(mean_g = mean(yi),
                   mean_vi = mean(vi),
                   range_min = range(yi)[1],
                   range_max = range(yi)[2],
                   quantile1 = quantile(yi)[1],
                   quantile2 = quantile(yi)[2],
                   quantile3 = quantile(yi)[3],
                   quantile4 = quantile(yi)[4],
                   quantile5 = quantile(yi)[5],
                   )
```

```{r}
ggplot(data, aes(x = yi, y = sample_size)) +
  geom_point(alpha = .4, shape = 1) +
  theme_classic()
```

<br>

### Outliers

There are some studies with very large Effect sizes >= 2 in the data
which might skew the ES estimates!

```{r}
data %>% 
  filter(yi > 2) %>% 
  arrange(desc(yi))
```

This is further investigated with GOSH plots in a previous rmd file


<br>
### Checking category names

```{r}
colnames(data)
```


```{r}
table(data$target_group)
target_group
```


```{r}
table(data$region)
region
```


```{r}
table(data$diagnosis)
diag
```


```{r}
table(data$type)
type
```


```{r}
table(data$format)
format
```


```{r}
table(data$control)
control
```


```{r}
table(data$risk_of_bias)
risk_of_bias
```

<br>


## Data with one outcome type 
```{r}
data_one_outcome_type <- mutate_all(data_2022_multiple_outcome_types_joined, 
                   funs(str_to_lower)) %>% 
  mutate(n_1 = as.numeric(ifelse(is.na(n_arm1), totaln_arm1, n_arm1)),
         n_2 = as.numeric(ifelse(is.na(n_arm2), totaln_arm1, n_arm2)),
         sample_size = n_1 + n_2,
         es_id = row_number() ,
         rob_include_best = ifelse(risk_of_bias == "low", 1, 0),
         rob_exclude_worst = ifelse(risk_of_bias %in% c("low", "some concern"), 1, 0)) %>% 
  select(study,
         es_id,
         yi, vi, sei,
         target_group, 
         format,
         diagnosis, 
         type,
         control, 
         region, 
         risk_of_bias, 
         rob,
         multiple_outcome_types,
         outlier,
         outlier_1.5_sd,
         rob_include_best,
         rob_exclude_worst,
         n_1, 
         n_2,
         sample_size)

data_one_outcome_type$vi <- as.numeric(data_one_outcome_type$vi)
data_one_outcome_type$yi <- as.numeric(data_one_outcome_type$yi)
data_one_outcome_type$sei <- as.numeric(data_one_outcome_type$sei)


data_one_outcome_type
```
<br>

```{r}
data_one_outcome_type <- data_one_outcome_type %>% filter(multiple_outcome_types == "select one outcome type")
```

### Sample size

```{r}
data_one_outcome_type %>% relocate(study, sample_size)
```

```{r}
data_one_outcome_type %>% 
  #group_by(study) %>%
  #distinct(sample_size) %>% 
  plyr::summarise(sample_size_sum = sum(sample_size, na.rm = T),
                  sample_size_median = median(sample_size, na.rm = T),
                  sample_size_mean = mean(sample_size, na.rm = T)) 
```

Individuals should be counted for the sample size and not multiple outcomes per person. Therefore I group by each study and keep only distinct sample sizes.

```{r}
sample_size_data <- data_one_outcome_type %>% 
  group_by(study) %>%
  distinct(sample_size) %>% 
  plyr::summarise(sample_size_sum = sum(sample_size, na.rm = T),
            sample_size_median = median(sample_size, na.rm = T),
            sample_size_mean = mean(sample_size, na.rm = T)) 

sample_size_data
```

<br>

### Included primary studies
```{r}
unique_studies <- length(unique(data_one_outcome_type$study))
unique_studies
```

<br>

### Effect size distribution
```{r}
data_one_outcome_type %>% 
  dplyr::summarise(mean_g = mean(yi),
                   mean_vi = mean(vi),
                   range_min = range(yi)[1],
                   range_max = range(yi)[2],
                   quantile1 = quantile(yi)[1],
                   quantile2 = quantile(yi)[2],
                   quantile3 = quantile(yi)[3],
                   quantile4 = quantile(yi)[4],
                   quantile5 = quantile(yi)[5],
                   )
```

```{r}
ggplot(data_one_outcome_type, aes(x = yi, y = sample_size)) +
  geom_point(alpha = .4, shape = 1) +
  theme_classic()
```

<br>

### Outliers

There are some studies with very large Effect sizes >= 2 in the data
which might skew the ES estimates!

```{r}
data_one_outcome_type %>% 
  filter(yi > 2) %>% 
  arrange(desc(yi))
```

This is further investigated with GOSH plots in a previous rmd file


<br>

## Saving final data
```{r}
write_csv(data, "data/tidy/data_cleaned_one_outcome_type.csv")

write_csv(data, "data/tidy/data_cleaned.csv")
```



