---
title: Introduction to the workshops
subtitle: Replicability Crisis in Science?
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE,
                      dev = "svg",
                      fig.align = "center")

library(kableExtra)
```

# About me {.section}

## About me {.about}

### Filippo Gambarota 

![[`r icons::fontawesome("envelope")`](mailto:filippo.gambarota@unipd.it) [`r icons::fontawesome("globe")`](filippogambarota.xyz) [`r icons::fontawesome("github")`](github.com/filippogambarota)  
](img/fg.jpg){width=200 fig-align="center"}

- [**Postdoctoral Researcher**]{.imp}: Department of Developmental and Social Psychology
- **Research interests**: meta-analysis, psychometrics, data simulation, R programming and multiverse analysis.

## About us {.about}

We are part of the **Psicostat** research group. A interdisciplinary research group interested in Psychology and Statistics. `r icons::fontawesome("globe")` [psicostat.dpss.psy.unipd.it](https://psicostat.dpss.psy.unipd.it/)

<center>
<iframe src="https://psicostat.dpss.psy.unipd.it/" style="width:1000px; height:500px"></iframe>
</center>

# Program {.section}

## Program

```{r}
#| echo: false
data.frame(
  stringsAsFactors = FALSE,
               Day = c("08/07/24", "09/07/24", "10/07/24"),
             Title = c("Tools for reproducible research",
                       "Statistical methods for replication assessment","Meta-analyis and multiverse analysis"),
            Topics = c("R, Quarto, Git/Github, Open Science Framework",
                       "Frequentist and Bayesian statistical methods for replicability assessment",
                       "Equal and random-effects model, heterogeneity, power-analysis, simulating data")
) |> 
kable()  |> 
kable_styling(full_width = FALSE, font_size = 25) |> 
column_spec(2, bold = TRUE)
```

## Materials 📘

. . .

- 🌐 All the **material** (code, slides, extra) are available on **Github** [github.com/stat-teaching/replicability-stat-unipd-phd](https://github.com/stat-teaching/replicability-stat-unipd-phd). The same material can be accessed using this link [stat-teaching.github.io/replicability-stat-unipd-phd](https://stat-teaching.github.io/replicability-stat-unipd-phd/)

. . .

- 📝 Slides are created with **Quarto**, you can use it as standard slides (in *html* format) and see the source code (`.qmd` file)

. . .

- 💻 For code debugging, exercises or general questions we can use this shared online code editor [etherpad.wikimedia.org/p/replicability-stat-unipd-phd](https://etherpad.wikimedia.org/p/replicability-stat-unipd-phd). Basically we can write code together `r emo::ji("smile")`

. . .

- ⚙️ We are going to use mainly the slides, R Studio, the Github website and the shared editor. **I suggest you to bookmark the Github website and the editor**

# The website {.section}

## Disclaimer

. . .

- We are using a lot of (R) code. When talking about code there is no a unique solution or method. My approach is not the best. If your code works, everything good :smile:

. . .

- If we have time, we can discuss about best practice in writing code in terms of efficency, organization and clarity :sunglasses:

. . .

- Also for statistics related topics, there are often multiple options to solve a problem. If you know other alternatives beyond the proposed topics, we can discuss it :wink:

# Let's start! {.section}